---
title: "A quick assessment of PECA networks on human complex traits"
author: "Xiang Zhu"
date: "2018-07-19"
output: workflowr::wflow_html
---

```{r, echo=FALSE}
suppressPackageStartupMessages(library(data.table))
suppressPackageStartupMessages(library(dplyr))
suppressPackageStartupMessages(library(knitr))
```

## PECA networks

Below is an example of PECA networks (courtesy of Duren).
Columns 1-6 are TG, RE, TF, corr(TG, RE), corr(TG, TF)
and combined p-value for corr(TG, RE) and corr(TG, TF). 

```{r, echo=FALSE}
options(width=300)
peca_net <- data.table::fread("~/Downloads/TissueNet_merged/Tissue_network_Ovary.txt")
dplyr::sample_n(peca_net,5)
```

There are 201 PECA networks, each corresponding to a tissue or cell type.

```{r, echo=FALSE}
sample_name <- scan("~/Dropbox/rss/Data/peca_human/out_market/sampleName",what="character",sep="\n")
net_info <- data.frame(sample_name=sample_name,net_id=(1:length(sample_name)),stringsAsFactors=FALSE)

dplyr::sample_n(net_info,5)
```

## Analysis methods

- Use PECA network to annotate SNPs: $a_j=1$ if SNP $j$ is inside any TG, RE and TF of a network.
- Apply a simple enrichment method from [Zhu and Stephens (2017)](https://doi.org/10.1101/160770)
to 201 PECA networks and 31 complex human traits (`r 201*31` analyses in total);
see [Supplementary Figure 17](https://www.biorxiv.org/content/biorxiv/suppl/2018/07/16/160770.DC2/160770-3.pdf) for details.
- Output a log10 likelihood ratio value to measure the strength of enrichment.

Some known limitations of this quick assessment:

- Ignore the difference among TG, RE and TF.
- Ignore the directionality among TG, RE and TF.
- Focus on 1.1 million HapMap3 common SNPs only.
- Unable to account for LD in a principled way.
- Unable to correct for general enrichments near genes (TG, TF) and regulatory regions (RE).
- Some tissues and cell types have multiple PECA networks.

This simple analysis yields some findings in concordance with literature:

- Age at natural menopause --- MCF-7 (breast cancer cell line)
- Crohn’s disease --- primary B cells from peripheral blood
- Gout --- Treg Primary Cells
- High-density lipoprotein --- HepG2 (liver cancer cell line)
- Rheumatoid arthritis --- CD8 Primary Cells

## Full results

```{r, echo=FALSE}
res_mat <- readRDS("~/Dropbox/rss/Data/peca_human/out_market/peca_human_ashlrt_20180719.rds")
res_df <- as.data.frame(res_mat/log(10), row.names=NULL)
res_df$net_id <- (1:201)
res_df <- dplyr::inner_join(net_info, res_df, by="net_id")
```

```{r, echo=FALSE, results="asis", eval=TRUE}
trait_set <- colnames(res_mat)
num_trait <- length(trait_set)
#num_trait <- 2 # for testing

for (j in 1:num_trait) {
  cat(paste0('### Complex trait: ',trait_set[j],'\n')) 
  tmp_df <- res_df[, c("sample_name","net_id",trait_set[j])]
  tmp_df <- tmp_df[order(tmp_df[[trait_set[j]]], decreasing=TRUE),]
  rownames(tmp_df) <- NULL
  print(knitr::kable(tmp_df))
  cat('\r\n\r\n')
}
```

